Checkpoint 4

### 2020-04-30 Checkpoint 4.Rmd
Update Checkpoint 4.Rmd

Variables of Interest: 
\
• per_capita_income
\
•totalTestResults
\
• StateColor
\
• percent_asian
\
•percent_black

@@

model_5 <- stan_glmer(
  ChinaVirusInterest ~ StateColor + (1 | State), #Gives us random intercepts
  data = Finaldata, family = gaussian, chains = 3, iter = 100*2
)
```

@@

ggplot(model_5_df, aes(x = correlation)) + 
  geom_density(alpha = 0.5)

@@

##Model 7: 
StateColor + percent_asian + (StateColor | State)

model_7 <- stan_glmer(
  ChinaVirusInterest ~ StateColor + percent_asian + (StateColor | State), #Gives us random intercepts
  data = Finaldata, family = gaussian, chains = 4, iter = 3000*2
)
```

```{r}
head(data.frame(summary(model_7)),-2)
```

```{r}
# y = original sample, yrep = MCMC simulation
set.seed(454)
pp_check(model_7, nreps = 50)
```

```{r}
# Store the chains
model_7_df <- as.array(model_7) %>% 
  melt %>% 
  pivot_wider(names_from = parameters, values_from = value)

# Wrangle the chains
# Note the need for `...` around the sigma_sq_b
model_7_df <- model_7_df %>% 
  mutate(sigma_sq_w = `sigma`, sigma_sq_b = `Sigma[State:(Intercept),(Intercept)]`) %>% 
  mutate(correlation = (sigma_sq_b/(sigma_sq_b+sigma_sq_w)))

ggplot(model_7_df, aes(x = correlation)) + 
  geom_density(alpha = 0.5)

```{r}
# set.seed(454)
# my_data <- data.frame(StateColor = "blue", State = "IL", percent_asian = .12)
# 
# # Simulate a set of predictions for each case in newdata
# my_prediction <- posterior_predict(
#   model_7,
#   newdata = my_data)

#my_prediction <- data.frame(y_new = my_prediction[,1])

#ggplot(my_prediction, aes(x = y_new)) +
 # geom_density()

#summary(my_prediction)
```

@@

```{r}
#set.seed(454)
#my_data <- data.frame(StateColor = "red", State = "FL")

# Simulate a set of predictions for each case in newdata
#my_prediction <- posterior_predict(
 # model_5, 
  #newdata = my_data)

#my_prediction <- data.frame(y_new = my_prediction[,1])

#ggplot(my_prediction, aes(x = y_new)) + 
 # geom_density()

#summary(my_prediction)
```

>>>>

@@

model_5 <- stan_glmer(
  ChinaVirusInterest ~ Day + StateColor + (Day | State), #Gives us random intercepts
  data = Finaldata, family = gaussian, chains = 4, iter = 5000*2
)
```

@@

ggplot(model_5_df, aes(x = correlation)) +
  geom_density(alpha = 0.5)
```

```{r}
#set.seed(454)
my_data <- data.frame(StateColor = "blue", State = "FL", Day = 18336)

@@

@@

# Simulate a set of predictions for each case in newdata
my_prediction <- posterior_predict(
  model_9,
   newdata = my_data)

ChinaVirusInterest ~ Day + StateColor + (Day | State)	mean	mcse	sd	X10.	X50.	X90.	n_eff	Rhat
	(Intercept)	-1.94E+04	4.20E+01	6.48E+03	-2.77E+04	-1.94E+04	-1.11E+04	23821
	Day	1.06E+00	2.29E-03	3.54E-01	6.06E-01	1.06E+00	1.51E+00	23821
	StateColorpurple	-4.47E-01	3.93E-02	3.96E+00	-5.46E+00	-4.45E-01	4.57E+00	10177
	StateColorred	-4.09E+00	3.24E-02	3.35E+00	-8.39E+00	-4.09E+00	1.79E-01	10690

ChinaVirusInterest ~ StateColor + percent_asian + (Day | State)								
	(Intercept)	4.36E+01	3.80E-02	3.16E+00	3.96E+01	4.35E+01	4.76E+01	6895
	StateColorpurple	-8.65E-01	5.00E-02	4.23E+00	-6.28E+00	-8.61E-01	4.40E+00	7182
	StateColorred	-4.48E+00	4.29E-02	3.68E+00	-9.18E+00	-4.50E+00	2.35E-01	7384
	percent_asian	-8.57E+00	3.33E-01	3.10E+01	-4.82E+01	-8.11E+00	3.03E+01	8710

ChinaVirusInterest ~ StateColor +percent_asian + totalTestResults + (StateColor | State)								
	(Intercept)	4.27E+01	7.19E-02	3.00E+00	3.90E+01	4.27E+01	4.65E+01	1741
	StateColorpurple	-2.52E-01	9.18E-02	4.05E+00	-5.38E+00	-2.01E-01	4.85E+00	1949
	StateColorred	-3.82E+00	9.17E-02	3.77E+00	-8.63E+00	-3.87E+00	8.40E-01	1685
	percent_asian	-1.07E+01	5.48E-01	2.86E+01	-4.61E+01	-1.05E+01	2.60E+01	2720
	totalTestResults	3.17E-04	4.75E-06	2.78E-04	-4.82E-05	3.19E-04	6.61E-04	3409
